\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-29 doc/USER_MANUAL/manual_SPECFEM3D.tex
updates SPECFEM3D configuration with scotch, manual and examples; further code clean up

\item [Numerical simulations in general] ~\\
Forward simulations are described in detail in \cite{TrKoLi08,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,KoGoErMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}. Additional aspects dealing with adjoint simulations are described in
\cite{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10}.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores in shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,KoGoErMi10,Kom11}.

@@

\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.0.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D\_V2.0.0} will then contain
the source code. To configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

The SCOTCH library \citep{PeRo96}
provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
A recent version of its source code is provided in directory \texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
The path to an existing SCOTCH installation can to be set with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-dir=/opt/scotch
\end{lyxcode}

@@

Prior to compiling \texttt{decompose\_mesh\_SCOTCH}, make sure you have correctly specified the path
of the SCOTCH library with the option \texttt{-{}-with-scotch-dir} of the \texttt{configure} script.
For convenience we provide the source code of SCOTCH, which is released open source under the French CeCILL-C version 1 license,
in directory ~\\
\texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}. Please refer to file INSTALL.txt in that directory to see how to compile it.
In the future you should be able to find more recent versions at  \url{http://www.labri.fr/perso/pelegrin/scotch/scotch\_en.html} .
\\

>>>>

\item [Numerical simulations in general] ~\\
Forward simulations are described in detail in \cite{TrKoLi08,VaCaSaKoVi99,KoMiEr09,KoErGoMi10,KoGoErMi10,ChKoViCaVaFe07,MaKoDi09,KoViCh10,CaKoLaTiMiLeSnTr08,TrKoHjLiZhPeBoMcFrTrHu10,KoRiTr02,KoTr02a,KoTr02b,KoTr99} or \cite{KoVi98}. Additional aspects dealing with adjoint simulations are described in
\cite{TrTaLi05,LiTr06,TrKoLi08,LiTr08,TrKoHjLiZhPeBoMcFrTrHu10}.
Domain decomposition is explained in detail in \cite{MaKoBlLe08}, and excellent scaling up to 150,000 processor cores is shown for instance in
\cite{CaKoLaTiMiLeSnTr08,KoLaMi08a,MaKoBlLe08,KoErGoMi10,KoGoErMi10,Kom11}.

@@

\begin{lyxcode}
{\small tar~-zxvf~SPECFEM3D\_V2.0.0.tar.gz}{\small \par}
\end{lyxcode}
The directory \texttt{\small SPECFEM3D} will then contain
the source code. To configure the software for your system, run the
\texttt{configure} shell script. This script will attempt to guess
the appropriate configuration values for your system. However, at
a minimum, it is recommended that you explicitly specify the appropriate
command names for your Fortran90 compiler and MPI package:

@@

The SCOTCH library \citep{PeRo96}
provides efficent static mapping, graph and mesh partitioning routines. SCOTCH is a free software package developed by
Fran\c {c}ois Pellegrini et al. from LaBRI and INRIA in Bordeaux, France, downloadable from the web page \url{https://gforge.inria.fr/projects/scotch/}. It is more recent than METIS, actively maintained and performs better in many cases.
A recent version of its source code is provided in directory \texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
In case no SCOTCH libraries can be found on the system, the configuration will bundle this version for compilation.
The path to an existing SCOTCH installation can to be set explicitly with the option \texttt{-{}-with-scotch-dir}. Just as an example:
\begin{lyxcode}
./configure~FC=ifort~MPIFC=mpif90~-{}-with-scotch-dir=/opt/scotch
\end{lyxcode}

@@

In most cases, the configuration with \texttt{./configure~FC=ifort} should be sufficient.
During the configuration process, the script tries to find existing SCOTCH installations. 
In case your system has no pre-existing SCOTCH installation,
we provide the source code of SCOTCH, which is released open source under the French CeCILL-C version 1 license,
in directory 
\texttt{src/decompose\_mesh\_SCOTCH/scotch\_5.1.10b}.
This version gets bundled with the compilation of the SPECFEM3D package if no libraries could have been found.
If this automatic compilation of the SCOTCH libraries fails,
please refer to file INSTALL.txt in that directory to see further details how to compile it on your system.
In case you want to use a pre-existing installation, make sure you have correctly specified the path
of the SCOTCH library when using the option \texttt{-{}-with-scotch-dir} with the \texttt{./configure} script.
In the future you should be able to find more recent versions at  \url{http://www.labri.fr/perso/pelegrin/scotch/scotch\_en.html} .
\\
